Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-30 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

\begin{definition}\cite{544199} Given a operator or matrix\nb$A$,
the norm of $A$ is defined by 
\begin{equation}
\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|\,.
\end{equation}
\end{definition}

The previously defined matrix norm is not one of the common matrix
norms as in the following example.

\begin{example}Consider $A=\left(\begin{array}{cc}
1 & 0\\
1 & 1
\end{array}\right)$. Then, 
\begin{equation}
\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|=\frac{3}{2}\,.
\end{equation}
\end{example}

@@

\begin{proof}Since
\begin{equation}
\frac{\delta}{d}\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
\end{equation}
we have
\begin{equation}
\frac{\delta}{d}\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\label{eq:Born_rule_difference}
\end{equation}
for all normalized pure state\nb$\ket{\psi}$.

>>>>

\begin{definition}\label{def:norm}\cite{544199} Given a operator
or matrix\nb$A$, the norm of $A$ is defined by 
\begin{equation}
\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|\,.
\end{equation}
\end{definition}

The previously defined matrix norm is not one of the common matrix
norms as shown in the following example.

\begin{example}Consider $A=\left(\begin{array}{cc}
1 & 0\\
1 & 1
\end{array}\right)$. It is easy to verify $\left\Vert A\right\Vert =3/2$. On the other
hand, its Frobenius norm or Hilbert-Schmidt norm
\begin{equation}
\left\Vert A\right\Vert _{\mathrm{F}}=\Tr\left(A^{\dagger}A\right)=\left(\sum_{i,j}\left|a_{ij}\right|^{2}\right)^{1/2}
\end{equation}
is $\sqrt{3}$\nb\cite{GolubVanLoan1996,Jaeger2007}, where $a_{ij}$
are the $\left(i,j\right)$-th entry of $A$; its operator $p$-norms
\begin{equation}
\left\Vert A\right\Vert _{p}=\sup_{\left\Vert \ket{\psi}\right\Vert _{p}=1}\left\Vert A\ket{\psi}\right\Vert _{p}=\sup_{\ket{\psi}\ne0}\left\Vert A\ket{\psi}\right\Vert _{p}/\left\Vert \ket{\psi}\right\Vert _{p}
\end{equation}
are $\left\Vert A\right\Vert _{1}=\left\Vert A\right\Vert _{\infty}=2$
and $\left\Vert A\right\Vert _{2}=\left[\left(3+\sqrt{5}\right)/2\right]^{1/2}$\nb\cite{RobertsVarberg1973,peres1995quantum,GolubVanLoan1996},
where $\ket{\psi}=\sum_{i=1}^{d}\alpha_{i}\ket{i}$, $\left\Vert \ket{\psi}\right\Vert _{\infty}=\max_{i}\left|\alpha_{i}\right|$,
and $\left\Vert \ket{\psi}\right\Vert _{p}=\left(\sum_{i=1}^{d}\left|\alpha_{i}\right|^{p}\right)^{1/p}$
for $1\le p<\infty$. The common matrix norms of $A$ are all different
from $3/2$ so that our norm defined in definition~\ref{def:norm}
is different from them.\end{example}

@@

\begin{proof}Since
\begin{equation}
\delta/d\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
\end{equation}
we have
\begin{equation}
\delta/d\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\label{eq:Born_rule_difference}
\end{equation}
for all normalized pure state\nb$\ket{\psi}$.
